---
title: "Capstone"
author: "Vlad Oles"
date: "April 28, 2015"
output: html_document
---
```{r, global_knitr_options, include = FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE,
                      fig.path = "../figures/firsttry_",
                      fig.height = 5, fig.weight = 11)
```

```{r, load_libraries, results = "hide", message = FALSE, warning = FALSE}
library(dplyr)
library(ggplot2)
source("functions.R")
```

```{r, load_data, results = "hide"}
gapminder <- read.csv("../data/gapminder.csv")
```

Here is the plot for China:
```{r, plot_china}
plot_country("China", gapminder, "green")
```

Here is the plot for India:
```{r, plot_india}
plot_country("India", gapminder, "red")
```

Here is the plot for USA:
```{r, plot_usa}
plot_country("United States", gapminder, "blue")
```

We can quite see how GDP increases as the time goes, and this trend is suprisingly common for all the countries.

```{r, life_exp_2007, include = FALSE}
  life_exp <- group_by(gapminder, continent) %>%
    summarize(avg = mean(lifeExp), min = min(lifeExp), max = max(lifeExp))
```
_Africa life expectancy:_ average - `r get_life_exp(life_exp, "Africa", "avg")`, minimal - `r get_life_exp(life_exp, "Africa", "min")`, maximal - `r get_life_exp(life_exp, "Africa", "max")`

_Asia life expectancy:_ average - `r get_life_exp(life_exp, "Asia", "avg")`, minimal - `r get_life_exp(life_exp, "Asia", "min")`, maximal - `r get_life_exp(life_exp, "Asia", "max")`

_Americas life expectancy:_ average - `r get_life_exp(life_exp, "Americas", "avg")`, minimal - `r get_life_exp(life_exp, "Americas", "min")`, maximal - `r get_life_exp(life_exp, "Americas", "max")`

_Europe life expectancy:_ average - `r get_life_exp(life_exp, "Europe", "avg")`, minimal - `r get_life_exp(life_exp, "Europe", "min")`, maximal - `r get_life_exp(life_exp, "Europe", "max")`

_Oceania life expectancy:_ average - `r get_life_exp(life_exp, "Oceania", "avg")`, minimal - `r get_life_exp(life_exp, "Oceania", "min")`, maximal - `r get_life_exp(life_exp, "Oceania", "max")`

Asia has the largest maximal value and at the same time second-to-smallest minimal value. Africa has the smallest in each of the aggregated values.

A histogram of global life expectancy with default bin width:
```{r, global_life_exp}
ggplot(gapminder, aes(x = lifeExp)) + geom_histogram(color = "black", fill = "lightblue")
```

A histogram of global life expectancy with narrower bin width:
```{r, global_life_exp_narrow}
ggplot(gapminder, aes(x = lifeExp)) + geom_histogram(binwidth = 1, color = "black", fill = "lightblue")
```

It seems like the first histogram has less precision, hence more countries falls under certain criterias.