---
title: "Capstone"
author: "Vlad Oles"
date: "April 28, 2015"
output: html_document
---
```{r, global_knitr_options, include = FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE,
                      fig.path = "../figures/firsttry_",
                      fig.height = 5, fig.weight = 11)
```

```{r, load_libraries, results = "hide", message = FALSE, warning = FALSE}
library(dplyr)
library(ggplot2)
source("functions.R")
```

```{r, load_data, results = "hide"}
gapminder <- read.csv("../data/gapminder.csv")
```

Here is the plot for China:
```{r, plot_china}
plot_country("China", gapminder, "green")
```

Here is the plot for India:
```{r, plot_india}
plot_country("India", gapminder, "red")
```

Here is the plot for USA:
```{r, plot_usa}
plot_country("United States", gapminder, "blue")
```

We can quite see how GDP increases as the time goes, and this trend is suprisingly common for all the countries.

Here we can see average and extremal values for life expectancies continent-wise. Asia has the largest maximal value and at the same time second-to-smallest minimal value. Africa has the smallest in each of the aggregated values.
```{r, life_exp_2007}
  group_by(gapminder, continent) %>%
    summarize(avg = mean(lifeExp), min = min(lifeExp), max = max(lifeExp))
```
